Algorithms for the Automated Correction of Vertical Drift in Eye Tracking Data

### 2020-10-19 manuscript/SI1.tex
Added stretch pseudocode

>>>>

\subsection{Stretch}

\noindent
\texttt{stretch} takes two additional arguments, \texttt{S} and \texttt{O}, which give the lower and upper bounds of the vertical scaling factor and vertical offset. \texttt{regress} calls on one external function, \texttt{minimize}, which minimizes the objective function \texttt{fit\_lines}. The \texttt{fit\_lines} function is nested inside the \texttt{stretch} function so that it inherits its lexical scope.

\begin{verbatim}
function stretch(fixation_XY, line_Y, S=[0.9,1.1], O=[-50,50])
|  n = length(fixation_XY)
|  fixation_Y = fixation_XY[:, 2]
|
|  function fit_lines(params, return_correction=FALSE)
|  |  candidate_Y = fixation_Y * params[1] + params[2]
|  |  corrected_Y = zeros(n)
|  |  for fixation_i in 1 : n
|  |  |  line_i = argmin(abs(line_Y - candidate_Y[fixation_i]))
|  |  |  corrected_Y[fixation_i] = line_Y[line_i]
|  |  if return_correction == TRUE
|  |  |  return corrected_Y
|  |  return sum(abs(candidate_Y - corrected_Y))
|
|  initial_params = [1, 0]
|  l_bounds = [S[1], O[1]]
|  u_bounds = [S[2], O[2]]
|  best_params = minimize(fit_lines, initial_params, l_bounds, u_bounds)
|  fixation_XY[, 2] = fit_lines(best_params, return_correction=TRUE)
|  return fixation_XY
\end{verbatim}
